# polling trends:

```{r}
library(pacman)
p_load(tidyverse, grid, ggnewscale, magrittr, lubridate)

# import data: ####
load("articles/RTcorpus.RData")
load("polls/all_polls.RData")

```


prepare helpers
```{r}
partycolors <- c("green", "red", "black", "yellow", "brown", "purple", "gray")
names(partycolors) <- c("gru", "spd", "cdu", "fdp", "afd", "lin", "oth")
candidatecolors <- c("green", "red", "black")
names(candidatecolors) <- c("baerbock", "scholz", "laschet")

parties <- c("cdu", "spd", "gru", "lin", "fdp", "afd", "oth")

```


get leading periods for each party (leaving out transition periods)
```{r}
# define background areas
rects_nogaps <- data.frame(ymin = rep(-100, 4), 
                           ymax = rep(Inf, 4), 
                           alpha = rep(.01, 4), 
                           xmin = as.Date(c("2020-12-01", "2021-04-26", "2021-05-16", "2021-08-24")), 
                           xmax = as.Date(c("2021-04-26", "2021-05-16", "2021-08-24", "2021-09-26")),
                           fill = c("gray40", "greenyellow", "gray40", "lightcoral")
)
rects_gaps <- data.frame(ymin = rep(-100, 4), 
                         ymax = rep(Inf, 4), 
                         alpha = rep(.01, 4), 
                         xmin = as.Date(c("2020-12-01", "2021-04-28", "2021-05-25", "2021-08-30")), 
                         xmax = as.Date(c("2021-04-21", "2021-05-08", "2021-08-18", "2021-09-26")),
                         fill = c("gray40", "greenyellow", "gray40", "lightcoral")
)
```


## plotting:

n### full polls of top3 parties
```{r}
(gg_leading_parties_trend <-
ggplot(polls_long %>% filter(party %in% parties[1:3]), 
       aes(colour = party, fill = party)) +
  geom_line(aes(x = date, y = mean)) +
#  geom_point(aes(x = date, y = percent)) +
  geom_ribbon(aes(date, ymin = lower, ymax = upper, colour = NULL), alpha = .1) +
  scale_fill_manual(aesthetics = c("colour", "fill"), values = partycolors[1:3]) +
#  layers$background +
#  coord_cartesian(ylim = c(0, 40)) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b")
) # %>% ggplotly(gg_all_parties_poll)
```


### polls of all parties
```{r warning=FALSE}
p_load(EBImage, ggimage)

polls_long %<>% mutate(images = case_when(
  party == "gru" & date == as.Date("2021-09-24")  ~ "D:/OneDrive - Hertie School/Hertie/Thesis/Bundestagswahl 2021 — RT DE_files/Baerbock_portrait_hoch.png",
  party == "spd" & date == as.Date("2021-09-24") ~ "D:/OneDrive - Hertie School/Hertie/Thesis/Bundestagswahl 2021 — RT DE_files/Scholz_portrait_hoch.png",
  party == "cdu" & date == as.Date("2021-09-24") ~ "D:/OneDrive - Hertie School/Hertie/Thesis/Bundestagswahl 2021 — RT DE_files/Laschet_portrait_hoch.png"
))

(gg_all_parties_trend <-
    ggplot(polls_long, 
           aes(colour = party, fill = party)) +
    geom_line(aes(x = date, y = mean), size = 2) +
    geom_ribbon(aes(date, ymin = lower, ymax = upper, colour = NULL), alpha = .4) +
  geom_image(aes(x = date, y = case_when(party == "spd" ~ mean + 2.5, 
                                         party == "cdu" ~ mean - .5, 
                                         TRUE ~ mean - .2), image = images, colour = NULL, fill = NULL), size = .08, fullpage = FALSE, scale_axes = TRUE, alpha = 1) +
    scale_fill_manual(aesthetics = c("colour", "fill"), values = partycolors) +
    coord_cartesian(ylim = c(5, 40)) + 
    scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    labs(x = "", y = "polling numbers [%]") +
    guides(fill = "none", colour = "none") +
   theme_minimal()
)

ggsave("../Bundestagswahl 2021 — RT DE_files/candidate_trends.png", width = 2250, height = 900, units = "px")

```



```{r}
# define layers to add to plots ####

layers <- vector('list')
layers$scalex <- scale_x_date(date_breaks = "1 month", date_labels = "%b")
layers$partycolors_all <- scale_fill_manual(aesthetics = c("colour", "fill"), values = partycolors)
layers$partycolors_three <- scale_fill_manual(aesthetics = c("colour", "fill"), values = partycolors[1:3])
layers$candidatecolors <- scale_fill_manual(aesthetics = c("colour", "fill"), values = candidatecolors)
layers$background <- geom_rect(data = rects_nogaps, mapping = aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = list("gray40", "greenyellow", "gray40", "lightcoral"), alpha = .01), show.legend = F)
layers$background_gaps <- geom_rect(data = rects_gaps, mapping = aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = list("gray40", "greenyellow", "gray40", "lightcoral"), alpha = .1), show.legend = F)
layers$newscale_fill <- ggnewscale::new_scale_fill()
layers$newscale_colour <- ggnewscale::new_scale_colour()
layers$trendline_three <- geom_line(data = polls_long %>% filter(party %in% parties[1:3]), mapping = aes(colour = party, x = date, y = mean))
layers$trends_ci_three <- geom_ribbon(data = polls_long %>% filter(party %in% parties[1:3]), mapping = aes(fill = party, x = date, ymin = lower, ymax = upper, colour = NULL), alpha = .2)
layers$articles_RT_candidates_n <- geom_smooth(data = summariesRT_long %>% filter(candidate != "all"), mapping = aes(x = date, y = articles, colour = candidate), se = F)
layers$articles_RT_candidates_perc <- geom_smooth(data = summariesRT_long %>% filter(candidate != "all"), mapping = aes(x = date, y = share, colour = candidate), se = F)
# producing graph backgrounds ####  

# leaving gaps where close
(gg_leading_party_background_gaps <- 
  ggplot() + 
  layers$background_gaps
)

# until clearly passed
(gg_leading_party_background <- 
  ggplot() +
  layers$background
)
```



### RT articles mentioning candidates over time:
```{r}
library(ggnewscale) 

gg_leading_party_background +
   new_scale_fill() +
   layers$candidatecolors +
  layers$scalex +
  layers$articles_candidates_n +
  # useful to make this a layer? 
  geom_smooth(data = summariesRT_long %>% filter(candidate == "all"), 
           mapping = aes(x = as.Date(date), y = articles), colour = "grey", linetype = "longdash") +
  coord_cartesian(ylim = c(0,3))
  
  # share of articles mentioning candidates (aka zooming in)
  gg_leading_party_background +
    new_scale_fill() +
    layers$articles_candidates_perc +
    coord_cartesian(ylim = c(0,.1)) +
    layers$candidatecolors
#  geom_smooth(data = summariesRT_long %>% filter(candidate != "all"), mapping = aes(x = date, y = share, colour = candidate), se = F)

```




# negativity distribution:
(gg_sent_score_text_source <- 
analysis_candidate_data %>% 
  ggplot() +
  geom_hline(aes(yintercept = 0)) +
  geom_violin(aes(x = source, y = article_sent_article, fill = source), scale = "count", draw_quantiles = .5, show.legend = F) +
  labs(x = "", y = "Sentiment score") +
  theme_minimal()
)


(gg_sent_score_headlead_source <- 
  analysis_data %>% 
  ggplot() +
  geom_hline(aes(yintercept = 0)) +
  geom_violin(aes(x = source, y = article_sent_headlead, fill = source), scale = "count", draw_quantiles = .5, show.legend = F) + 
  scale_fill_brewer(palette = "Set2") +
  labs(x = "", y = "Sentiment score") +
  theme_minimal()
)
  
# time-series (average sentiment, pos/neg-classification per period)

Difference:
```{r}
load("analyses/diff_by_day.RData")

diff_by_day %<>% mutate(period_red  = ifelse(period == "red_period", 1, 0),
                        period_green  = ifelse(period == "green_period", 1, 0),
                        period_black  = ifelse(period == "black_period", 1, 0), 
                        pre_campaign = ifelse(as.Date(date, origin = as.Date("2021-01-01")) < as.Date("2021-04-19"), 1, 0),
                        post_campaign = ifelse(as.Date(date, origin = as.Date("2021-01-01")) > as.Date("2021-09-26"), 1, 0),
                        date = as.numeric(date - min(date)), 
                        own_period = case_when(candidatename == "baerbock" & period_green == 1 ~ 1,
                                               candidatename == "scholz" & period_red == 1 ~ 1,
                                               candidatename == "laschet"  & period_black == 1 ~ 1, 
                                               TRUE ~ 0),
                        
                        rank_top = case_when(candidatename == "baerbock" & rank_gru == 1 ~ 1,
                                             candidatename == "scholz" & rank_spd == 1 ~ 1,
                                             candidatename == "laschet" & rank_cdu == 1 ~ 1,  
                                             TRUE ~ 0),
                        
                        
                        gru_spd = share_gru - share_spd,
                        gru_cdu = share_gru - share_cdu,
                        spd_cdu = share_spd - share_cdu,
                        
                        rank_top2 = case_when(candidatename == "baerbock" & rank_gru < 3 ~ 1,
                                              candidatename == "scholz" & rank_spd < 3 ~ 1,
                                              candidatename == "laschet"  & rank_cdu < 3 ~ 1,
                                              candidatename == "baerbock" & is.na(rank_gru) ~ NaN,
                                              candidatename == "scholz" & is.na(rank_spd) ~ NaN,
                                              candidatename == "laschet"  & is.na(rank_cdu) ~ NaN,
                                              TRUE ~ 0),
                        
                        relative_share = case_when(candidatename == "baerbock" ~ gru_cdu + gru_spd,
                                                   candidatename == "scholz" ~ spd_cdu + spd_gru,
                                                   candidatename == "laschet" ~ cdu_gru + cdu_spd, 
                                                   TRUE ~ NaN
                        ),
                        
                        candidatename = factor(candidatename, levels = c( "none", "scholz", "laschet", "baerbock")),
                        
                        baerbock = ifelse(candidatename == "baerbock", 1, 0),
                        laschet = ifelse(candidatename == "laschet", 1, 0),
                        scholz = ifelse(candidatename == "scholz", 1, 0)
                        
)
```


plot it:

```{r warning=FALSE}
diff_by_day %>% filter(candidatename != "none") %>% 
  ggplot(aes(x = as.Date(date, origin = "2021-01-04"), 
             y = overall_sent, 
             colour = factor(own_period))) +
  geom_smooth(formula = "y ~ poly(x, 2)")

diff_by_day %>% filter(candidatename != "none") %>% 
  ggplot(aes(x = as.Date(date, origin = "2021-01-04"), 
             y = N, 
             colour = factor(own_period))) +
  geom_smooth(formula = "y ~ poly(x, 2)")

diff_by_day %>% filter(candidatename != "none") %>% 
  ggplot(aes(x = as.Date(date, origin = "2021-01-04"), 
             y = .$negative_binary_article_relative, 
             colour = factor(own_period))) +
  geom_smooth(formula = "y ~ poly(x, 2)")


diff_by_day %>% filter(candidatename != "none") %>% group_by(own_period) %>%  
  ggplot(aes(x = as.Date(date, origin = "2021-01-04"), 
             y = .$negative_count_article, 
             colour = factor(rank_top))) +
  geom_smooth(formula = "y ~ poly(x, 2)") +
  geom_point(alpha = .1) 

# +  coord_cartesian(ylim = c(-1, 1))



gg_leading_party_background +
  geom_smooth(aes(x = as.Date(date, origin = "2021-01-04"), 
             y = negative_mentions, 
             colour = factor(rank_top)),
             se = FALSE, formula = "y ~ poly(x, 2)",
             data = diff_by_day %>% filter(candidatename != "none" & pre_campaign == 0 & post_campaign == 0) %>% group_by(own_period)) +
  geom_point(alpha = .1) +
   scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    labs(x = "", y = "over-coverage (mentions in negative context)", colour = "Leading candidate") +
    theme_minimal() +  
  coord_cartesian(ylim = c(-21, 3), xlim = c(as.Date("2021-04-26"), as.Date("2021-09-26")))


gg_leading_party_background +
  ggnewscale::new_scale_color() +
  geom_smooth(aes(x = as.Date(date, origin = "2021-01-04"), 
             y = negative_mentions, 
             colour = factor(candidatename)), 
             se = FALSE, formula = "y ~ poly(x, 2)",
             size = 1.5,
             data = diff_by_day %>% filter(candidatename != "none" & pre_campaign == 0 & post_campaign == 0 & negative_mentions != 0) %>% group_by(candidatename)) +
  geom_point(aes(x = as.Date(date, origin = "2021-01-04"), 
             y = negative_mentions, 
             colour = factor(candidatename)), 
             alpha = .2, 
             size = 1.5,
             data = diff_by_day %>% filter(candidatename != "none" & pre_campaign == 0 & post_campaign == 0 & negative_mentions != 0) %>% group_by(candidatename)) +  
  scale_fill_manual(aesthetics = c("colour"), values = candidatecolors[1:3]) +
  coord_cartesian(ylim = c(-21, 3), xlim = c(as.Date("2021-04-26"), as.Date("2021-09-26"))) +
  labs(x="", y="Difference in negative \ndaily candidate mentions") +
  guides (colour = "none") +
  theme_minimal()
ggsave("../Bundestagswahl 2021 — RT DE_files/reporting_trends.png", width = 2250, height = 900, units = "px")

  
```

  






